Using reference models in feature selection problems \vspace{.1in}

### 2019-10-15 paper/ref_approach.tex
rewriting and reordering

\usepackage{soul}
\usepackage{mathtools}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{graphicx,pdflscape}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{float}
\usepackage{supertabular}
%\usepackage{booktabs,caption,fixltx2e}
\usepackage{booktabs,fixltx2e}
\usepackage[font={small,it}]{caption}
\usepackage{tcolorbox}
\usepackage{paralist}
\usepackage{multicol}
\setcitestyle{round}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\theoremstyle{definition}
\newtheorem{example}{Example}

@@

\begin{document}
\maketitle
\begin{abstract}
  Feature selection, or more generally, model reduction is an important aspect of statistical workflow aiming to provide insights from data. In this paper we discuss and demonstrate the benefits of using a reference model in model selection in general. A reference model acts as a noise-filter on the target variable by modeling its data generation mechanism. Using the reference model predictions in the model selection reduces the variability and improves stability leading to improved model selection performance. Assuming that a Bayesian reference model describes well the future data distribution, it can be shown that decision theoretically justified approach is to project the reference model to a reduced model leading to projection predictive variable selection approach. The reference model can be used also ad-hoc in combination of common feature selection methods.  In several numerical experiments, we demonstrate superior performance of projection predictive approach and show how use of a reference model translates into better and more stable feature selection independently of the specific selection procedure. 
% These benefits are also illustrated on a real-world example of predicting the amount of body fat for which we compare a reference model based selection method to a purely data driven approach.
\end{abstract}

@@

In data based approaches, such as Lasso selection
\citep{tibshirani1996regression} or stepwise backward/forward
regression \citep{venables2013modern,harrell2015regression}, the
observed empirical data distribution is utilised as a proxy of future
data usually in combination with cross-validation or information
criteria to provide estimates for out-of-sample predictive
performance.  In contrast, reference model based methods approximate
the future data generation mechanism using the predictive distribution
of a reference model, which can be, for example, a full-encompassing
model including all covariates.  The main assumption under any
reference model approach is that we operate in an
$\mathcal{M}$-\textit{complete} framework
\citep{book:bernardo_smith,vehtari2012survey}, that is we have
constructed a model which reflects in the best way our beliefs about
the future data and which has passed model checking and criticism
\citep[see, e.g.][]{gelman2013bayesian}.  The reference model approach
has been used for long time in Bayesian statistics since the seminal
work of \citet{paper:reference_lindley}. For more historical
references, see papers by \citet{vehtari2012survey} and
\citet{paper:model_selection}, and for most recent methodological
development see \citet{paper:projpred}.

@@

To motivate the further discussion and experiments, we start by simple
example comparing projection predictive approach (projpred,
\citet{paper:projpred}) which uses a reference model and classic
stepwise backward regression (steplm).  using the body fat data
\citep{johnson1996fitting}\footnote{The analysis is based on
  \texttt{R}-notebook by Vehtari available at
  \url{https://avehtari.github.io/modelselection/bodyfat.html}.}.  The
experiments are implemented in \texttt{R} \citep{Rcore2018}.

The target variable of interest is the amount of body fat, which is
measured by immersing a person in water tank which is a complex and
expensive procedure. Additionally, we have information about 13
covariates which are anthropometric measurements (e.g., height, weight
and thicknes of skin and fat in different body locations). The
covariates are are highly correlated whichs causes additional
challenge in the model selection. In total, we have 251
observations. The goal is to find the model which is able to predict
the amount of fat sufficiently well while requiring least amount of
measurements for a new person.

\cite{paper:bodyfat} report results using steplm with a significance
level of 0.157 with AIC selection \citep{akaike1974new}, fixing
abdomen and height to be always included in the model. For better
comparison we don't fix any of the variables.  The steplm approach is
carried out combining the \texttt{step} and \texttt{lm} functions

For the selection via projpred, the Bayesian reference model includes
all the covariates using a regularised horseshoe prior on the
covariate coefficients \citep{paper:rhs}. Submodels are explored using
forward search (the results are not sensitive to whether forward or
backward search is used), and the predictive utility is the expected
log-predictive density (elpd) estimated using PSIS-LOO
\citep{paper:psis_loo}.  We select the submodel as the one with the
smallest size which has an elpd score higher (i.e., better) than the
reference model score with probability of at least 5\%. See Appendix A
for brief review of projection predictive approach and papers by
\citet{paper:model_selection} and \citet{paper:projpred} for more
details. projpred selection is made using the \texttt{projpred} package.

@@

\begin{table}[tp]
\scriptsize
\centering
\begin{tabular}{l||l|r||l|r}
  \hline
M & projpred & Freq (\%) & steplm & Freq (\%)  \\ 
  \hline
1 & abdomen, weight & 39 & abdomen, age, forearm, height, hip, neck, thigh, wrist & 4 \\
2 & abdomen, wrist & 10 & abdomen, age, chest, forearm, height, neck, thigh, wrist & 4 \\
3 & abdomen, height & 10 & abdomen, forearm, height, neck, wrist & 2 \\
4 & abdomen, height, wrist & 9 & abdomen, forearm, neck, weight, wrist & 2 \\
5 & abdomen, weight, wrist & 8 & abdomen, age, height, hip, thigh, wrist & 2 \\
6 & abdomen, chest, height, wrist & 2 & abdomen, age, height, hip, neck, thigh, wrist & 2 \\
7 & abdomen, biceps, weight, wrist & 2 & abdomen, age, ankle, forearm, height, hip, neck, thigh, wrist & 2 \\
8 & abdomen, height, weight, wrist & 2 & abdomen, age, biceps, chest, height, neck, wrist & 2 \\
9 & abdomen, age, wrist & 2 & abdomen, age, biceps, chest, forearm, height, neck, thigh, wrist & 2 \\
10 & abdomen, age, height, neck, thigh, wrist & 2 & abdomen, age, ankle, biceps, weight, wrist & 2 \\
   \hline
\end{tabular}
\caption{Bootstrap model selection frequencies after 100 bootstrap samples.}
\label{tab:model_frequencies}
\end{table}

@@

\begin{table}[tp]
\scriptsize
\centering
\begin{tabular}{l|r|r|r|r}
  \hline
 & RMSE(Full) & RMSE(Sel) & Size(Sel) & SizeIr(Sel) \\ 
  \hline
projpred & 4.35 & 4.47 & 2 & -  \\
steplm & 4.38 & 4.47 & 7 & - \\
\hline
\hline
projpred & 4.58 & 4.54 & 2 & 0  \\
steplm & 5.89 & 5.43 & 19 & 13 \\
   \hline
\end{tabular}
\caption{Model predictive performances with original data (first two
  rows) and adding noisy features (last two rows) estimated with
  10-fold cross-validation. Abbreviations: Full = full model; Sel =
  selected submodel; Size = total number of included covariates;
  SizeIr = number of included irrelevant covariates.}
\label{tab:model_performances}
\end{table}

Both projpred and steplm compare a large number of models using either
forward or backward search, which can lead to selection induced
overfitting, but even with 100 covariates projpred is able to select a
submodel with similar performance as the full model. Although projpred
uses Bayesian inference and steplm maximum likelihood, it is not
decisive feature explaining the difference in the performance.  The
main difference between the approaches is whether a reference model is
used or not, and in the rest of the paper we look into more detail how
the use of reference model helps and limitations of the approach.

@@

A properly designed reference model is able to filter parts of the
noise present in the data, and hence provide an improved and more
stable selection process. This holds even if the reference model does
not perfectly resemble the true data generating process. Moreover, our
analyses indicate that the substantial reduction of variance
attributable to noise is usually more important than small potential
bias due to model misspecification.  We argue that, regardless of how
the reference model is set up and used in the inference procedure, it
can be always seen as acting as a filter on the observed
data. Furthermore, regardless of what specific model selection method
is used, a reference model can be used instead of raw data during the
selection process to improve the stability and selection
performance. Our results indicate that the core reason why the
reference model based methods perform well is the reference model
itself, rather than the specific way of using it.  In general, the
less data we have and the more complex the estimated models, the
higher the benefit of using a reference models as the basis for
variable selection.

@@

\hypertarget{comparison-minimal-subset}{
\section{A comparison for the minimal subset selection}\label{comparison-minimal-subset}}

Addressing the problem of selecting the minimal subset of relevant/predictive features, 
we compare with a simulation study the selection via projection predictive approach, 
via stepwise forward selection with/without a reference model on top and a Bayesian 
stepwise forward selection.
\begin{itemize}
\item projpred (ref model based): reference model is a linear regression over the first 
five supervised principal components, search heuristics is forward search and the predictive 
performance is estimated via 10-fold cross-validation.
\item stepwise selection (data based): it's based on AIC comparison
\item stepwise selection (ref model based): reference model is a linear regression 
over the first five SPC. The reference model point predictions (posterior predictive means $\hat{y}$) 
are used instead of the target variable values $y$. Based on AIC comparison
\item Bayesian stepwise selection (data based): At each step the model fitted is a 
linear regression using RHS prior and the feature excluded is the one with higher 
Bayesian p-value, defined as:
\begin{equation}
\text{Bayesian p-value}(\theta) := \text{min}\{P(\theta\leq0|D),P(\theta>0|D)\}
\end{equation}
The selection continues if the reduced model has an elpd score higher than the
current fitted model.
\item Bayesian stepwise selection (ref model based): same as the data based, but instead of using the observed data values to fit the models at each step, it uses the observed covariate and the target values predicted by a reference model 
\end{itemize}

We simulate data according to \eqref{eq:simulated_data} fixing the overall number of 
features equal to $p=100$ with $k=20$ of them being predictive. In Figure \ref{fig:rmse_vs_fdr} 
it is shown, for different values of $n$ and $\rho$, the predictive performance in terms of 
root mean square error and the false discovery rate of the selected submodel, averaged after 100 data simulations.
Figure \ref{fig:entropy} reports the entropy scores for the different methods compared. Lower entropy corresponds to
a more stable selection. Highly correlated predictive features may happen to be alternately selected, making the measure of
the stability of the selection a non-trivial task. Entropy suffers of such a problem, thus such a measure should be seen
as one of different possible measurements of the actual stability. We note that the reference model approach slightly improves 
with respect to the corresponding data based methods, whereas the projection predictive approach results to be far more stable
than all the other ones.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/rmse_vs_fdr_parallel.pdf}
  \caption{Root mean square error (RMSE) against false discovery rate for the minimal subset of feature selection.\\}
  \label{fig:rmse_vs_fdr}
\end{figure}

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/entropy_parallel.pdf}
  \caption{Entropy score for the minimal subset of feature selection.\\}
  \label{fig:entropy}
\end{figure}

\hypertarget{comparison}{%
\section{A comparison in the normal means problem framework}\label{comparison}}

In this section, we analyse in more detail the benefits of reference
model approaches in combination of a few common variable selection
approach.

@@

@@

\subsection{Model selection approach to be compared}

The Bayesian estimation methods we use to solve the normal means
problem have in common that first a Bayesian regression model is
fitted using some sparsifying prior on the regression coefficients,
for example, as discussed in \cite{paper:dirichlet_laplace},
\cite{bhadra2017horseshoe+} and \cite{johnstone2004needles}.  In our
experiments, we include the Dirichlet-Laplace
\cite[DL;][]{paper:dirichlet_laplace} prior and the regularised
horseshoe (RHS) prior \citep{paper:rhs}, which we think scales better
to higher number of covariates as compared to other horseshoe-like
priors.

Within the set of complete selection procedures, we consider three
Bayesian methods.  \cite{johnstone2004needles} use a spike-and-slab
type prior given by a mixture of a delta distribution in zero and a
heavy-tailed distribution \cite[see
also][]{paper:spike_slab_mitchell}. When the latter is a Laplace
distribution, they show an interesting thresholding property of the
median estimator and, based on this observation, present a complete
selection procedure using their prior. We refer to this method as
EB.med. Further, we use a method to control for the local false
discovery rate (loc.fdr) as described in \cite{paper:efron,
  efron2012large}. Finally, we device a simple selection procedure
based on posterior credible intervals using the regularised horseshoe
prior in which we select covariates whose 90\% credible intervals
excludes zero (ci.90). All of these methods provide a complete
selection procedure and we compare their performance with and without
using a reference model on top of them. As criteria of selection
performance, we evaluate the average false discovery rate (i.e., the
ratio of the number of non-relevant selected features over the number
of selected features) and the average sensitivity (i.e., the ratio of
the number of relevant selected features over the total number of
relevant features). We also provide a comparison of the stability of
the selection by means of a stability measure proposed by
\cite{paper:stability}. Table \ref{tab:comparison} summarises the
methods used in the numerical experiments.

@@

\hypertarget{complete-selection}{%
\subsubsection{Complete selection analysis}\label{complete-selection}}
As complete selection procedures we consider the control of the local
false discovery rate \citep{paper:efron, efron2012large}, the
empirical Bayes median \citep{johnstone2004needles}, the selection
by posterior credible intervals and an adaptation of the projection 
predictive approach that we name iterative projection.\

The selection
by 90\% posterior credible intervals is done using the regularised
horseshoe prior and selecting those features whose posterior
distribution does not include zero in the interval between the 5\% and
the 95\% quantiles.

The iterative projection is a tentative to adapt the projection predictive 
approach to select the whole set of relevant features. Applying the straightforward 
implementation of projpred, we are able to select a minimal subset of features, which
yield to a model with a predictive performance comparable to the full model one.
The iterative projection repeats the projpred selection for different iterations, at each time
excluding from the search path the features selected in the previous steps. At each iteration
the selected submodel size corresponds to the one having a predictive performance close enough
to the baseline model, which in this iterative version is the submodel with the highest predictive
score explored at the current iteration. The stopping rule that we adopted is the following:
\begin{equation} 
\label{eq:rule_of_thumb}
\text{min} \{i\in \{0,..,p\}: \text{P}(\text{elpd}_{i}-\text{elpd}_{\text{best}}>0)\geq \alpha \}
\end{equation}
where $i$ indexes the submodel size and ``best'' stays for the best predictive explored submodel
at the considered iteration. The algorithm terminates when the empty model (only intercept) satisfies
the stopping rule.
The choice of the hyperparameter $\alpha$ can be non-trivial, we have 
observed sensitivity of the selection to such a choice mainly when using cross-validation with a small
number of observations or not very predictive features. 
In our experiments we chose the default value used in the \texttt{projpred} 
\texttt{R}-package that corresponds to $\alpha=0.16$.
\hl{NOTE: if necessary I can add a pseudo-code illustration of the iterative projection algorithm, as 
I did in the thesis}

@@

>>>>

\usepackage{soul}
\usepackage{mathtools}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{graphicx,pdflscape}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{float}
\usepackage{supertabular}
%\usepackage{booktabs,caption,fixltx2e}
\usepackage{booktabs,fixltx2e}
\usepackage[font={small,it}]{caption}
\usepackage{tcolorbox}
\usepackage{paralist}
\usepackage{multicol}
\setcitestyle{round}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\theoremstyle{definition}
\newtheorem{example}{Example}
\newcommand{\note}[1]{\textcolor{red}{#1}}

@@

\begin{document}
\maketitle
\begin{abstract}
  Feature selection, or more generally, model reduction is an important aspect of statistical workflow aiming to provide insights from data. In this paper we discuss and demonstrate the benefits of using a reference model in feature selection. A reference model acts as a noise-filter on the target variable by modeling its data generating mechanism. Use of the reference model predictions in the model selection reduces the variability and improves stability leading to improved model selection performance. Assuming that a Bayesian reference model describes well the future data distribution, it can be shown that decision theoretically justified approach is to project the reference model to a reduced model leading to projection predictive variable selection approach. The reference model can be used also ad-hoc in combination with common feature selection methods.  In several numerical experiments, we demonstrate superior performance of projection predictive approach and show how use of a reference model translates into better and more stable feature selection independently of the specific selection procedure. 
% These benefits are also illustrated on a real-world example of predicting the amount of body fat for which we compare a reference model based selection method to a purely data driven approach.
\end{abstract}

@@

In data based approaches, such as Lasso selection
\citep{tibshirani1996regression} or stepwise backward/forward
regression \citep{venables2013modern,harrell2015regression}, the
observed empirical data distribution is utilised as a proxy of future
data usually in combination with cross-validation or information
criteria to provide estimates for out-of-sample predictive
performance.  In contrast, reference model based methods approximate
the future data generation mechanism using the predictive distribution
of a reference model, which can be, for example, a full-encompassing
model including all covariates.  The main assumption under any
reference model approach is that we operate in an
$\mathcal{M}$-\textit{complete} framework
\citep{book:bernardo_smith,vehtari2012survey}, that is, we have
constructed a model which reflects in the best way our beliefs about
the future data and which has passed model checking and criticism
\citep[see, e.g.][]{gelman2013bayesian}.  The reference model approach
has been used for long time in Bayesian statistics since the seminal
work of \citet{paper:reference_lindley}. For more historical
references, see papers by \citet{vehtari2012survey} and
\citet{paper:model_selection}, and for most recent methodological
development see \citet{paper:projpred}.

@@

To motivate the further discussion and experiments, we start by simple
example comparing projection predictive approach (\emph{projpred},
\citet{paper:projpred}) which uses a reference model and classic
stepwise backward regression (steplm).  using the body fat data
\citep{johnson1996fitting}\footnote{The analysis is based on
  \texttt{R}-notebook by Vehtari available at
  \url{https://avehtari.github.io/modelselection/bodyfat.html}.}.  The
experiments are implemented in \texttt{R} \citep{Rcore2018}.

The target variable of interest is the amount of body fat, which is
measured by immersing a person in water tank which is a complex and
expensive procedure. Additionally, we have information about 13
covariates which are anthropometric measurements (e.g., height, weight
and thicknes of skin and fat in different body locations). The
covariates are are highly correlated which causes additional
challenge in the feature selection. In total, we have 251
observations. The goal is to find the model which is able to predict
the amount of fat sufficiently well while requiring least amount of
measurements for a new person.

\cite{paper:bodyfat} report results using \emph{steplm} with a significance
level of 0.157 with AIC selection \citep{akaike1974new}, fixing
abdomen and height to be always included in the model. For better
comparison we don't fix any of the variables.  The steplm approach is
carried out combining the \texttt{step} and \texttt{lm} functions

For the selection via projpred, the Bayesian reference model includes
all the covariates using a regularised horseshoe prior on the
covariate coefficients \citep{paper:rhs}. Submodels are explored using
forward search (the results are not sensitive to whether forward or
backward search is used), and the predictive utility is the expected
log-predictive density (elpd) estimated using PSIS-LOO
\citep{paper:psis_loo}.  We select the submodel as the one with the
smallest size which has an elpd score similar to the reference model
when taking into account the uncertainty in estimating the predictive
model performance. See Appendix A for brief review of projection
predictive approach and papers by \citet{paper:model_selection} and
\citet{paper:projpred} for more details. projpred selection is made
using the \texttt{projpred} package.

@@

\begin{table}[tp]
\scriptsize
\centering
\begin{tabular}{l|lr|lr}
%  \hline
M & projpred & Freq \% & steplm & Freq \%  \\ 
  \hline
1 & abdom, weight & 39 & abdom, age, forearm, height, hip, neck, thigh, wrist & 4 \\
2 & abdom, wrist & 10 & abdom, age, chest, forearm, height, neck, thigh, wrist & 4 \\
3 & abdom, height & 10 & abdom, forearm, height, neck, wrist & 2 \\
4 & abdom, height, wrist & 9 & abdom, forearm, neck, weight, wrist & 2 \\
5 & abdom, weight, wrist & 8 & abdom, age, height, hip, thigh, wrist & 2 \\
6 & abdom, chest, height, wrist & 2 & abdom, age, height, hip, neck, thigh, wrist & 2 \\
7 & abdom, biceps, weight, wrist & 2 & abdom, age, ankle, forearm, height, hip, neck, thigh, wrist & 2 \\
8 & abdom, height, weight, wrist & 2 & abdom, age, biceps, chest, height, neck, wrist & 2 \\
9 & abdom, age, wrist & 2 & abdom, age, biceps, chest, forearm, height, neck, thigh, wrist & 2 \\
10 & abdom, age, height, neck, thigh, wrist & 2 & abdom, age, ankle, biceps, weight, wrist & 2 \\
%   \hline
\end{tabular}
\caption{Bootstrap model selection frequencies after 100 bootstrap samples.}
\label{tab:model_frequencies}
\end{table}

@@

\begin{table}[tp]
\scriptsize
\centering
\begin{tabular}{ll|rrrr}
%  \hline
Data  & Method & RMSE Full & RMSE Selected & \# Selected & \# Selected noisy \\ 
  \hline
original & projpred & 4.35 & 4.47 & 2 &   \\
& steplm & 4.38 & 4.47 & 7 &  \\
\hline
+ noisy features & projpred & 4.58 & 4.54 & 2 & 0  \\
& steplm & 5.89 & 5.43 & 19 & 13 \\
%   \hline
\end{tabular}
\caption{Model predictive performances with original data (first two
  rows) and with extra noisy features (last two rows) estimated with
  10-fold cross-validation. Abbreviations: Full = full model; Selected =
  selected submodel; \# Selected = total number of features selected;
  \# Selected noisy = number of extra noisy features selected.}
\label{tab:model_performances}
\end{table}

Both projpred and steplm compare a large number of models using either
forward or backward search, which can lead to selection induced
overfitting, but even with 100 covariates projpred is able to select a
submodel with similar performance as the full model. Although projpred
uses Bayesian inference and steplm maximum likelihood, it is not
here the decisive feature explaining the difference in the performance.  The
main difference between the approaches is whether a reference model is
used or not, and in the rest of the paper we look into more detail how
the benefits and limitations of the reference model approach.

@@

A properly designed reference model is able to filter parts of the
noise present in the data, and hence provide an improved and more
stable selection process. This holds even if the reference model does
not perfectly resemble the true data generating process. Moreover, our
analyses indicate that the substantial reduction of variance
attributable to noise is usually more important than small potential
bias due to model misspecification.  We argue that, regardless of how
the reference model is set up and used in the inference procedure, it
can be always seen as acting as a filter on the observed
data. Furthermore, regardless of what specific model selection method
is used, a reference model can be used instead of raw data during the
selection process to improve the stability and selection
performance. Our results indicate that the core reason why the
reference model based methods perform well is the reference model
itself, rather than the specific way of using it.  In general, the
less data we have and the more complex the estimated models, the
higher the benefit of using a reference models as the basis for
feature selection.

@@

\hypertarget{comparison-minimal-subset}{
\section{Minimal subset feature selection}\label{comparison-minimal-subset}}

In the bodyfat example above we desired at the same time good
predictive performance and selection of a smaller number of
features. When the goal is to select a minimal subset of features
which have similar predictive performance as the full model we call it
\emph{minimal subset feature selection}. This minimal subset might
exclude features which have some predictive information about the
target, but given the minimal subset these features are nit able to
provide such additional information which would improve predictive
performance. The usual reason for this is that the relevant features
not in the minimal subset highly correlate with features already in
the minimal subset. We will later return to a problem of finding all
the features with some predictive power.

Using the data generating mechanism \eqref{eq:simulated_data}, we
simulate data sets of different size with a relatively large number of
features $p=100$ with with $k=20$ of them being predictive.
We compare the minimal subset feature selection perfomance of
projection predictive approach (with a reference model), a Bayesian
stepwise forward selection (without a reference model), and stepwise
forward selection with and without a reference model.
\begin{itemize}
\item projpred: The reference model is a Bayesian linear regression
  model (ie, the posterior predictive distributions are used) using
  the first five supervised principal components. The search heuristic
  is forward search, and the predictive performance is estimated via
  10-fold cross-validation.
\item steplm (data based): Stepwise selection using AIC as in the bodyfat example.
\item steplm using a reference model: The reference model is the same as for projpred, but only point predictions (posterior predictive means) $\hat{y}$ are used to replace the target variable $y$. Same AIC selection is used in data based steplm.
\item Bayesian stepwise selection (data based): At each step the model
  fitted is a Bayesian linear regression using regularised horseshoe
  prior and the feature excluded is the one with higher Bayesian
  $p$-value, defined as:
\begin{equation}
\text{Bayesian p-value}(\theta) := \text{min}\{P(\theta\leq0|D),P(\theta>0|D)\}
\end{equation}
The selection continues if the reduced model has an elpd score higher than the
current fitted model.
\item Bayesian stepwise selection (ref model based): same as the data based, but instead of using the observed data values to fit the models at each step, it uses the observed covariate and the target values predicted by a reference model 
\end{itemize}

In Figure \ref{fig:rmse_vs_fdr} it is shown, for different values of
$n$ and $\rho$, the predictive performance in terms of root mean
square error and the false discovery rate of the selected submodel,
averaged after 100 data simulations. projpred has superior FDR and the
smallest RMSE. Using a reference model improves steplm significantly,
but the minimal subset feature selection stays unreliable. Stepwise
Bayesian linear regression model without a reference model is better
than steplm without a reference model, but the minimal subset feature
selection is unreliable.

Figure \ref{fig:entropy} reports the entropy scores for the different
methods compared. Lower entropy corresponds to a more stable
selection. Highly correlated predictive features may happen to be
alternately selected, making the measure of the stability of the
selection a non-trivial task. Entropy suffers of such a problem, thus
such a measure should be seen as one of different possible
measurements of the actual stability. The use of a reference model
improves slightly stability of steplm in feature selection. The
projection predictive approach results to be far more stable than all
the other ones. This is likely due to as projpred is based on better
decision theoretical formulation which 1) takes into account the full
predictive distribution and not just point estimate and 2) projects
the reference model posterior to the submodel instead of using a
simple refit of submodels.

% TODO: Bigger and more distinctive symbols in figures
% label order: steplm, bayes.step, projpred
\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/rmse_vs_fdr_parallel.pdf}
  \caption{Root mean square error (RMSE) against false discovery rate in the minimal subset feature selection.}
  \label{fig:rmse_vs_fdr}
\end{figure}

% TODO: Bigger and more distinctive symbols in figures
% TODO: order steplm, bayes.step, projpred
\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/entropy_parallel.pdf}
  \caption{Entropy score in the minimal subset feature selection.}
  \label{fig:entropy}
\end{figure}

% \hypertarget{comparison}{%
%   \section{A comparison in the normal means problem framework}\label{comparison}}
\section{Complete feature selection}

Alternative to minimal subset feature selection is \emph{complete
  feature selection}, in which the goal is to find all relevant
features which have some predictive information about the target. In
complete feature selection it is possible that there are theoretically
relevant features, but given finite noisy data we are not able infer
these effects.

The projection predictive approach was designed for the minimal subset
feature selection, but here examine its performance also in complete
feature selection. In addition, we analyse the benefits of reference
model approach in combination of a few common complete feature
selection approaches.

\subsection{Complete feature selection approaches to be compared}

Many Bayesian approaches for complete feature selection first fit a
Bayesian regression model using some sparsifying prior on the
regression coefficients, for example, as discussed in
\cite{paper:dirichlet_laplace}, \cite{bhadra2017horseshoe+} and
\cite{johnstone2004needles}.  In our experiments, we include the
Dirichlet-Laplace \cite[DL;][]{paper:dirichlet_laplace} prior and the
regularised horseshoe (RHS) prior \citep{paper:rhs}, which we think
scales better to higher number of covariates as compared to other
horseshoe-like priors.
\note{Aki: How this paragraph connects to the next paragraph?}

Within the set of complete selection procedures, we consider three
Bayesian methods.  \cite{johnstone2004needles} use a spike-and-slab
type prior given by a mixture of a delta distribution in zero and a
heavy-tailed distribution \cite[see
also][]{paper:spike_slab_mitchell}. When the latter is a Laplace
distribution, they show an interesting thresholding property of the
median estimator and, based on this observation, present a complete
selection procedure using their prior. We refer to this method as
\emph{EB.med}. Further, we use a method to control for the local false
discovery rate (\emph{loc.fdr}) as described in \cite{paper:efron,
  efron2012large}. Finally, we device a simple selection procedure
based on posterior credible intervals using the regularised horseshoe
prior in which we select covariates whose 90\% credible intervals
excludes zero (\emph{ci.90}) \note{Reference for this?}.

All of these methods provide a complete selection procedure and we
compare their performance with and without using a reference model.
\note{Aki: Explain here how the reference mdoels are used for these. Point
  estimates replace data?}

As criteria of selection performance, we evaluate the average false
discovery rate (i.e., the ratio of the number of non-relevant selected
features over the number of selected features) and the average
sensitivity (i.e., the ratio of the number of relevant selected
features over the total number of relevant features). We also provide
a comparison of the stability of the selection by means of a stability
measure proposed by \cite{paper:stability}. Table \ref{tab:comparison}
summarises the methods used in the numerical experiments.

\note{Aki: ``Type: Complete selection'' doesn't make sense in the table. Maybe we need to discuss when to use the term complete selection and what is the alternative title for this section.}

\hypertarget{complete-selection}{%
\subsection{Details of methods?}\label{complete-selection}}

\note{Should this be combined with previous subsection?}

As complete selection procedures we consider the control of the local
false discovery rate \citep{paper:efron, efron2012large}, the
empirical Bayes median \citep{johnstone2004needles}, the selection
by posterior credible intervals and an adaptation of the projection 
predictive approach that we name iterative projection.\

The selection
by 90\% posterior credible intervals is done using the regularised
horseshoe prior and selecting those features whose posterior
distribution does not include zero in the interval between the 5\% and
the 95\% quantiles. \note{Reference?}

We can use the projection predictive approach for complete feature
selection by using it iteratively.  Applying the straightforward
implementation of projpred, we are able to select a minimal subset of
features, which yield to a model with a predictive performance
comparable to the full model one.  The iterative projection repeats
the projpred selection for different iterations, at each time
excluding from the search the features selected in the previous
iterations. At each iteration the selected submodel size corresponds to the
one having a predictive performance close enough to the baseline
model, which in this iterative version is the submodel with the
highest predictive score explored at the current iteration. The
stopping rule that we adopted is the following:
\begin{equation} 
\label{eq:rule_of_thumb}
\text{min} \{i\in \{0,..,p\}: \text{P}(\text{elpd}_{i}-\text{elpd}_{\text{best}}>0)\geq \alpha \}
\end{equation}
where $i$ indexes the submodel size and ``best'' stays for the best predictive explored submodel
at the considered iteration. The algorithm terminates when the empty model (only intercept) satisfies
the stopping rule.
The choice of the hyperparameter $\alpha$ can be non-trivial, we have 
observed sensitivity of the selection to such a choice mainly when using cross-validation with a small
number of observations or not very predictive features. 
In our experiments we chose the default value used in the \texttt{projpred} 
\texttt{R}-package that corresponds to $\alpha=0.16$.
\hl{NOTE: if necessary I can add a pseudo-code illustration of the iterative projection algorithm, as 
I did in the thesis}

@@

\note{Aki: Why two subsections on simulated data? Combine this with next one, or did I understand their contents wrong?}

@@

@@

\subsection{Simulation results of complete feature selection}

@@

\note{Aki: Is this only complete feature selection or also more results for the minimal subset feature selection?}
